Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

The quantity of actions for a node over time is a discrete function, so we
cannot define its deriviation $f(t,v)=\frac{\mathrm{d}}{\mathrm{d}t}k(G_t,v)$
directly. However, we reverse this property, and let $\int_{-\infty}^t
f(\tau,v)\mathrm{d}\tau\approx k(G_t,v)$, then $f$ will prove soundness
representing the change rate of degree.

@@

Then we move on the dynamic centrality, by extending the often used model
for static network named Katz centrality\cite{katz1953new}, which is actually
a generalized version of eigenvalue centrality which estimate the influence
of a node in social networks by counting the total number of walks between a pair of
node. We try to combine the activity and the clasical centrality metric and
expect to define a new centrality model that is mode sensitive to immediate
effect.

@@

Now from
\begin{equation}
z(t)=
\begin{cases}
z(t_k)+t-t_k&  t\in (t_k, t_{k+1})\\
z(t_{k+1})+t-t_{k+1}& t\in (t_{k+1}, t_{k+2})
\end{cases}
\end{equation}

we have:
\begin{equation}
\begin{split}
&\int_{t_k}^{t_{k+2}} \mu^{\frac{1}{z(t)}} \mathrm{d}t\\
\ge{}& \int_{t_k}^{t_{k+1}^*} \mu^{\frac{1}{z(t)}} \mathrm{d}t \\
={}&\int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}
\mathrm{d}t+ \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}}\\& -
\mu^{\frac{1}{z(t_{k+1})}} \mathrm{d}t + (t_{k+1}^*-t_{k+1})\mu^{\frac{1}{z(t_{k+1})}}\\
\ge{}& \int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} -
\mu^{\frac{1}{z(t_{k})}}\mathrm{d}t + \int_{t_{k+1}}^{t_{k+1}^*}
\mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} - \mu^{\frac{1}{z(t_{k+1})}}\mathrm{d}t,
\end{split}
\end{equation}
by an easy induction, one can split a "phase" into integrals in the form 
\begin{equation}
\int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}\mathrm{d}t
\end{equation}
 Since $ \mu^{1/z}$ decreases as $z$ becomes larger, we can reduce it to the base case now.

@@

\item \textit{father}[$1\dots|V|$], an array exploited by the historicall
union-find algorithm\cite{tarjan1975efficiency} (a weakened model), which
will be discussed later. Each of the elements contains:
\begin{itemize}
\item $u$, the identity of $v_i$'s father node if $u>0$, otherwise $v_i$
is a root node, and $-u$ is the size of the tree.
\item $t$, the time when $u$ becomes non-zero.
\end{itemize}

@@

\begin{algorithm}[htbp]
\caption{\textsc{Modify Eta}($\eta'$)}
\label{alg-eta}
\textbf{Time Complexity:} $O(1)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\State $\eta\gets\eta'$;\State\Comment{Imcompatible with historical queries.
The alternative is to rebuild the whole graph.}
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[htbp]
\caption{\textsc{Query Centrality}($t$,$\alpha$,$\beta$,
$\mathbf{x}_0$,$m$)}
\label{alg-cen}
\textbf{Time Complexity:} $O(mK|V|)$, $K$ is the sparsity constant.\\
\textbf{Additional Space:} $O(|V|)$
\begin{algorithmic}[1]
\Require $0<\alpha<\lambda_1(A^\bullet(G_t))^{-1}$ and $\beta>0$ and $m>0$. Here
$\lambda_1(A)$ is the maximal possitive eigenvalue of matrix $A$.
\Ensure return the active centrality $\mathbf{x}(G_t)$.
\For{$i\gets 1\dots|V|$}
\State $a[i]\gets \Call{Query Activity}{t,v_i}$;
\State $d[i]\gets \mathrm{size}(\mathit{edgeListReduced}[i])$;
\State $\mathbf{x}[i]\gets \mathbf{x}_0[i]$;
\EndFor
\For{$\mathit{count}\gets 1\dots m$}
\For{$i\gets 1\dots|V|$}
\State $\mathbf{x'}[i]\gets \beta$;
\EndFor
\For{$i\gets 1\dots|V|$}
\ForAll{$j\in\mathit{edgeListReduced}[i]$}
\State $\mathbf{x'}[i]\gets \mathbf{x'}[i]+\alpha\cdot
a[j]\cdot\mathbf{x}[j]/d[j]$
\EndFor\EndFor
\For{$i\gets 1\dots|V|$}
\State $\mathbf{x}[i]\gets \mathbf{x'}[i]$;
\EndFor
\EndFor
\State\Return{$\mathbf{x}$};
\end{algorithmic}
\end{algorithm}

@@

\section{Experiment}
\subsection{Data Generation} 
Our data generation is base on real social networks provided by \cite{database1,
database2}. Unfortunately, those databases do not contain evolving history
recorded data, so we simulate the evolving history by use the
authentic graph as the final state of the tested dynamic graph.
We give a random permutation to the edges, in a way such that:
\begin{itemize}
\item There will always
be just one component -- known as the giant component. We never add an edge out
of the giant component, so the evolving of the network seems to have increasing
vertices joining to the network.
\item The time delay of two adjacent new edges is inversely proportional to the
size of the giant component. So the average activity of any indivitual node do
not change tremendously.
\end{itemize}
Because the final state
is from real world data, it is ensured 
the evolving graph generated by our model will satisfy all the property that we
discussed in section 2.2. In addition, Kumar introduced how to generate
an artificial evolving social networks\cite{kumar2010structure}.

>>>>

The quantity of actions for a node over time is a discrete function, so we
cannot define its derivation $f(t,v)=\frac{\mathrm{d}}{\mathrm{d}t}k(G_t,v)$
directly. However, we reverse this property, and let $\int_{-\infty}^t
f(\tau,v)\mathrm{d}\tau\approx k(G_t,v)$, then $f$ will prove soundness
representing the change rate of degree.

@@

Then we move on the dynamic centrality, by extending the often used model
for static network named Katz centrality\cite{katz1953new}, which is actually
a generalized version of eigenvalue centrality which estimate the influence
of a node in social networks by counting the total number of walks between a pair of
node. We try to combine the activity and the classical centrality metric and
expect to define a new centrality model that is mode sensitive to immediate
effect.

@@

Now from
\begin{equation}
z(t)=
\begin{cases}
z(t_k)+t-t_k&  t\in (t_k, t_{k+1})\\
z(t_{k+1})+t-t_{k+1}& t\in (t_{k+1}, t_{k+2}),
\end{cases}
\end{equation}
we have:
\begin{equation}
\begin{split}
&\int_{t_k}^{t_{k+2}} \mu^{\frac{1}{z(t)}} \mathrm{d}t\\
\ge{}& \int_{t_k}^{t_{k+1}^*} \mu^{\frac{1}{z(t)}} \mathrm{d}t \\
={}&\int_{t_k}^{t_{k+1}} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}
\mathrm{d}t+ \int_{t_{k+1}}^{t_{k+1}^*} \mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}}\\& -
\mu^{\frac{1}{z(t_{k+1})}} \mathrm{d}t + (t_{k+1}^*-t_{k+1})\mu^{\frac{1}{z(t_{k+1})}}\\
\ge{}& \int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} -
\mu^{\frac{1}{z(t_{k})}}\mathrm{d}t + \int_{t_{k+1}}^{t_{k+1}^*}
\mu^{\frac{1}{z(t_{k+1})+t-t_{k+1}}} - \mu^{\frac{1}{z(t_{k+1})}}\mathrm{d}t,
\end{split}
\end{equation}
by an easy induction, one can split a "phase" into integrals in the form 
\begin{equation}
\int_{t_k}^{t_{k}^*} \mu^{\frac{1}{z(t_k)+t-t_k}} - \mu^{\frac{1}{z(t_{k})}}\mathrm{d}t
\end{equation}
 Since $ \mu^{1/z}$ decreases as $z$ becomes larger, we can reduce it to the base case now.

@@

\item \textit{father}[$1\dots|V|$], an array exploited by the historical
union-find algorithm\cite{tarjan1975efficiency} (a weakened model), which
will be discussed later. Each of the elements contains:
\begin{itemize}
\item $u$, the identity of $v_i$'s father node if $u>0$, otherwise $v_i$
is a root node, and $-u$ is the size of the tree.
\item $t$, the time when $u$ becomes non-zero.
\end{itemize}

@@

\begin{algorithm}[htbp]
\caption{\textsc{Modify Eta}($\eta'$)}
\label{alg-eta}
\textbf{Time Complexity:} $O(1)$\\
\textbf{Additional Space:} $O(1)$
\begin{algorithmic}[1]
\State $\eta\gets\eta'$;\State\Comment{Incompatible with historical queries.
The alternative is to rebuild the whole graph.}
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[htbp]
\caption{\textsc{Query Centrality}($t$,$\alpha$,$\beta$,
$\mathbf{x}_0$,$m$)}
\label{alg-cen}
\textbf{Time Complexity:} $O(mK|V|)$, $K$ is the sparsity constant.\\
\textbf{Additional Space:} $O(|V|)$
\begin{algorithmic}[1]
\Require $0<\alpha<\lambda_1(A^\bullet(G_t))^{-1}$ and $\beta>0$ and $m>0$. Here
$\lambda_1(A)$ is the maximal positive eigenvalue of matrix $A$.
\Ensure return the active centrality $\mathbf{x}(G_t)$.
\For{$i\gets 1\dots|V|$}
\State $a[i]\gets \Call{Query Activity}{t,v_i}$;
\State $d[i]\gets \mathrm{size}(\mathit{edgeListReduced}[i])$;
\State $\mathbf{x}[i]\gets \mathbf{x}_0[i]$;
\EndFor
\For{$\mathit{count}\gets 1\dots m$}
\For{$i\gets 1\dots|V|$}
\State $\mathbf{x'}[i]\gets \beta$;
\EndFor
\For{$i\gets 1\dots|V|$}
\ForAll{$j\in\mathit{edgeListReduced}[i]$}
\State $\mathbf{x'}[i]\gets \mathbf{x'}[i]+\alpha\cdot
a[j]\cdot\mathbf{x}[j]/d[j]$
\EndFor\EndFor
\For{$i\gets 1\dots|V|$}
\State $\mathbf{x}[i]\gets \mathbf{x'}[i]$;
\EndFor
\EndFor
\State\Return{$\mathbf{x}$};
\end{algorithmic}
\end{algorithm}

@@

\section{Experiment}
\subsection{Data Generation} 
Our data generation is base on real social networks provided by \cite{database1,
database2}. Unfortunately, those databases do not contain evolving history
recorded data, so we simulate the evolving history by use the
authentic graph as the final state of the tested dynamic graph.
We give a random permutation to the edges, in a way such that:
\begin{itemize}
\item There will always
be just one component -- known as the giant component. We never add an edge out
of the giant component, so the evolving of the network seems to have increasing
vertices joining to the network.
\item The time delay of two adjacent new edges is inversely proportional to the
size of the giant component. So the average activity of any individual node
would not change tremendously.
\end{itemize}
Because the final state
is from real world data, it is ensured 
the evolving graph generated by our model will satisfy all the property that we
discussed in section 2.2. In addition, Kumar introduced how to generate
an artificial evolving social networks\cite{kumar2010structure}.
